Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-08-01 literature/paper_draft.qmd
minor change

```{r}
plot_relative_improvement <- function(MSE_data) {
  MSE_data |>
    filter(
      .model != "mint_true",
      h <= 4
    ) |>
    group_by(series, h) |>
    mutate(
      base_MSE = MSE[.model == "base"]
    ) |>
    ungroup() |>
    group_by(.model, h) |>
    summarise(
      MSE = mean(MSE),
      base_MSE = mean(base_MSE),
      pct_change = (MSE - base_MSE) / base_MSE * 100
    ) |>
    ggplot(aes(x = h, y = pct_change, color = .model)) +
    geom_line() +
    labs(
      x = "Forecast Horizon (h)",
      y = "Percentage Change (%)"
    ) +
    # labs(x = element_blank(), y = element_blank()) +
    theme_minimal()
}
```

@@

```{r}
#| label: fig-sim-results-dsp
#| fig-cap: "Relative improvement of the MSE of reconciled forecasts over the base forecasts for the 50x2 hierarchical structure with dense and sparse DGP's correlation matrix, for 1 to 4 steps ahead forecasts, with 2 time series lengths (T = 54 and T = 304)."
#| fig.height: 10
#| fig.width: 10
#| out.width: "90%"
#| fig.align: "center"
p_dense_50 <- sim_dense_50$MSE |>
  transform_sim_MSE(F) |> 
  plot_relative_improvement() +
    labs(title = "Dense DGP Covariance Matrix", subtitle = "T = 54")
p_sparse_50 <- sim_sparse_50$MSE |>
  transform_sim_MSE(F) |> 
  plot_relative_improvement() +
    labs(title = "Dense DGP Covariance Matrix")

>>>>

```{r}
plot_relative_improvement <- function(MSE_data) {
  MSE_data |>
    filter(
      .model != "mint_true",
      h <= 4
    ) |>
    group_by(series, h) |>
    mutate(
      base_MSE = MSE[.model == "base"]
    ) |>
    ungroup() |>
    group_by(.model, h) |>
    summarise(
      MSE = mean(MSE),
      base_MSE = mean(base_MSE),
      pct_change = (MSE - base_MSE) / base_MSE * 100
    ) |>
    ggplot(aes(x = h, y = pct_change, color = .model)) +
    geom_line() +
    labs(
      x = "Forecast Horizon (h)",
      y = "Percentage Change (%)"
    ) +
    # labs(x = element_blank(), y = element_blank()) +
    theme_bw()
}
```

@@

```{r}
#| label: fig-sim-results-dsp
#| fig-cap: "Relative improvement of the MSE of reconciled forecasts over the base forecasts for the 50x2 hierarchical structure with dense and sparse DGP's correlation matrix, for 1 to 4 steps ahead forecasts, with 2 time series lengths (T = 54 and T = 304)."
#| fig.height: 7
#| fig.width: 8
#| out.width: "90%"
#| fig.align: "center"
p_dense_50 <- sim_dense_50$MSE |>
  transform_sim_MSE(F) |> 
  plot_relative_improvement() +
    labs(title = "Dense DGP Covariance Matrix", subtitle = "T = 54")
p_sparse_50 <- sim_sparse_50$MSE |>
  transform_sim_MSE(F) |> 
  plot_relative_improvement() +
    labs(title = "Dense DGP Covariance Matrix")
